Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'

### 2023-10-04 supplements/supplements.tex
ready for first round of co-author feedback

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'},
  pdfauthor={Julia Prein1, Manuel Bohn1, Steven Kalinke1, \& Daniel B. M. Haun1},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'}
\author{Julia Prein\textsuperscript{1}, Manuel Bohn\textsuperscript{1}, Steven Kalinke\textsuperscript{1}, \& Daniel B. M. Haun\textsuperscript{1}}
\date{}

@@

\authornote{

Correspondence concerning this article should be addressed to Julia Prein, Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany. E-mail: \href{mailto:julia_prein@eva.mpg.de}{\nolinkurl{julia\_prein@eva.mpg.de}}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

\hypertarget{effects-of-trial-type-and-trial-number}{%
\section{Effects of trial type and trial number}\label{effects-of-trial-type-and-trial-number}}

Children showed nearly perfect precision in the first training trial. As visual access to the target location decreased in the succeeding training trials, imprecision levels increased. Within test trials, children's imprecision levels did not vary as a function of trial number.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_trainingtrials}

@@

\caption{\textbf{Imprecision by trial type, split by study version and sample}. The x axis represents the trial type. The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center. Small dots show the imprecision for each subject in each trial. Boxplots (boxes represent first to third quartiles of data; vertical lines indicate the median; horizontal black lines display the range) and a half violin plot show the data distribution.}\label{fig:fig1}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_acrosstrials}

@@

\caption{\textbf{Imprecision across test trials, split by study version and sample}. The x axis represents trial number. The y axis represents imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked one target width to the left or right of the true target center. The black dashed regression lines show smooth conditional means based on linear models. Small colored dots show the imprecision for each subject in each trial. Colored lines connect the trials of each individual.}\label{fig:fig2}
\end{figure}

@@

\hypertarget{webcam-coding-of-the-child-sample}{%
\section{Webcam coding of the child sample}\label{webcam-coding-of-the-child-sample}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_webcamcoding}

\caption{\textbf{Model comparison for exploratory webcam coding of parental interference}. Factors of parental interference and their influence on the probability of responding correctly. The graph shows the estimated density curves of a model's predictor coefficient. Models are ordered according to their WAIC scores in the trial-by-trial analysis, with the uppermost winning the model comparison. (A) Analysis on a trial-by-trial level. (B) Analysis on a subject level (i.e., average across trials per subject).}\label{fig:fig3}
\end{figure}

Comparing the performances of children across our two data collection modes, we found that children participating remotely were slightly more precise.
This difference was especially prominent in younger participants in the box version of the task.
It is conceivable that caregivers were especially prone to influence the behavior of younger children.
In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.
In an exploratory analysis, we coded parental behavior and environmental factors during remote unsupervised testing.
Due to the time consuming nature of hand coding videos frame by frame, we focused on the subsample with the greatest performance difference between data collection modes: the three-year-olds in the box version of the task (n = 16).
We reasoned that if parental interference cannot explain the greatest performance difference in our sample, the effects would be negligible in the remaining sample.
A trial was defined as the time between two eye blinking sounds.
We transcribed all utterances by parents and children and counted the words uttered by each.
We then classified the utterances into several categories: question asked by child, repeated test questions by caregiver, hints towards agents (how many times the caregivers guided the child's attention to the agent), hints towards eyes (how many times the caregivers guided the child's attention to the agent's eyes), verification of choice (how many times the caregiver questioned or double checked the child's response), mentioning of screen (how many times the caregiver verbally guided the child's attention to the screen), pointing to screen (how many times the caregiver pointed towards the screen), positive \& negative feedback, motivational statements, and incomprehensible utterances.
In addition, we coded how many adults and children were present, whether a response click was obviously conducted by the caregiver themselves, and whether children took a break during the trial.
We conducted a model comparison to estimate the effects of parental interference.
Our null model explained the response behavior by age, while including random effects for subject and target position (model notation in \texttt{R:\ correct\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ (1\ +\ symmetricPosition\ \textbar{}\ subjID)}.

We compared this null model to models including the number of words uttered by the caregiver, number of repeated testquestions, verification of choice, or hints towards eyes as fixed effects.
Furthermore, we calculated an parental interference index by summing up number of repeated testquestions, verification of choice, and hints towards eyes, with the sign matching the variable's direction of effect.
Remaining variables that we coded for were not included since there was not enough variation and/or occurrences in our sample.
We compared models using WAIC (widely applicable information criterion) scores and weights.
As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.
On the trial level, the model including the verification of choice as a main effect performed best: here, the less the caregivers asked for children's responses again, the more likely children clicked on the correct box.
Interestingly, the effect reversed on a subject level - possibly due to greater learning effects for the children that were most likely to click incorrectly in the beginning and then receiving most parental comments.
On the subject level, the model including number of repeated test questions performed best: the more caregivers asked again where the target landed, the more likely children were to respond to the incorrect box.
In all cases, however, ELPD difference scores were smaller than their standard errors.
Similarly, 95\% CI of the model estimates included zero and were rather wide.
Therefore, we conclude that the effect of parental interference was negligable and could, most likely, be explained as described above.

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
By trial - \# Verification choice & 255.98 & 15.66 & 0.34 & 0.00 & 0.00\\
By trial - Null model & 256.77 & 15.05 & 0.23 & -0.40 & 1.18\\
By trial - Parental interference index & 257.24 & 15.32 & 0.18 & -0.63 & 0.99\\
By trial - \# Repeated testquestion & 258.57 & 15.25 & 0.09 & -1.30 & 1.23\\
By trial - \# Words uttered by caregiver & 258.88 & 15.37 & 0.08 & -1.45 & 1.13\\
\addlinespace
By trial - \# Hints eyes & 258.88 & 15.35 & 0.08 & -1.45 & 1.21\\
By subject - \# Repeated testquestion & 83.61 & 10.23 & 0.81 & 0.00 & 0.00\\
By subject - Parental interference index & 88.27 & 12.17 & 0.08 & -2.33 & 3.58\\
By subject - Null model & 89.16 & 11.21 & 0.05 & -2.78 & 3.60\\
By subject - \# Verification choice & 89.96 & 12.04 & 0.03 & -3.18 & 4.47\\
\addlinespace
By subject - \# Words uttered by caregiver & 90.56 & 10.70 & 0.02 & -3.48 & 4.23\\
By subject - \# Hints eyes & 93.02 & 11.84 & 0.01 & -4.71 & 3.76\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{reliability-by-age-group}{%
\section{Reliability by age group}\label{reliability-by-age-group}}

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/tango_supplements_reli_byagegroup}

\caption{\textbf{Reliability split by age group}. (A) Internal consistency (odd-even split) in hedge child sample by age group. (B) Test-retest reliability in hedge child sample by age group. (C) Internal consistency (odd-even split) in box child sample by age group. (D) Test-retest reliability in box child sample by age group. For the hedge version, performance is measured as imprecision, i.e., the absolute distance between the target's center and the participant's click (averaged across trials). The unit of imprecision is counted in the width of the target, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. For the box version, performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that contained the target. Regression lines with 95\% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with \emph{Pearson}'s correlation coefficient \emph{r}. Dots show the performance for each subject. The color of data points denotes age group.}\label{fig:fig4}
\end{figure}

\hypertarget{validity}{%
\section{Validity}\label{validity}}

\hypertarget{social-environmental-factors}{%
\subsection{Social-environmental factors}\label{social-environmental-factors}}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We included all children where families filled out a short demographic questionnaire. This subsample consisted of 109 children, including 30 3-year-olds (mean = 41.80 months, SD = 3.44, range = 36 - 47),
36 4-year-olds (mean = 54.19 months, SD = 3.08, range = 48 - 59), and
43 5-year-olds (mean = 66.28 months, SD = 3.62, range = 60 - 71).

\hypertarget{analysis}{%
\subsubsection{Analysis}\label{analysis}}

To estimate social environmental influences on gaze understanding, we fitted GLMMs predicting the task performance by each of our questionnaire variables, controlling for age (scaled), data collection mode (reference category: remote unsupervised) and study version (reference category: box version): \texttt{cor\_tango\ \textbar{}\ trials(n\_tango)\ \textasciitilde{}\ age\ +\ datacollection\ +\ studyversion}).
In order to combine data of our two study versions, we transformed continuous click responses from the hedge version into a discrete outcome.
For the target position, we categorized two adjacent bins as one imaginary box.
To measure participants' performance, we created imaginary box boundaries around the target's landing position and examined whether the participant's click response fell into this imaginary box.
Across the two study versions, we could consequently model the number of participant's correct responses using a \texttt{Binomial} distribution.
For model comparisons, we ran separate models, each with one of the following predictors as a fixed effects added to the null model: number of household members, number of children aged 0-18 in household, number of children aged 1-12 in household, hours spent in childcare each day, and age when subject entered childcare.
In addition, we calculated three index scores.
First, we calculated a sibling variety score according to Peterson (2000).
Second, we implemented the modified version of Cassidy, Fineberg, Brown, and Perkins (2005).
Third, based on our own data exploration, we calculated the amount of peer exposure determined as the number of siblings and the average hours spent in childcare.
We compared the models using WAIC (widely applicable information criterion) scores and weights (McElreath, 2020).
As an indicator of out-of-sample predictive accuracy, lower WAIC scores stand for a better model fit.
WAIC weights represent the probability that the model in question provides the best out-of-sample prediction compared to the other models.

\hypertarget{results}{%
\subsubsection{Results}\label{results}}

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrr}
\toprule
Predictor & WAIC & SE\_WAIC & Weight & ELPD\_DIFF & SE\_ELPD\_DIFF\\
\midrule
Age of childcare entry & 571.62 & 28.13 & 0.73 & 0.00 & 0.00\\
Null model & 575.96 & 30.44 & 0.08 & -2.17 & 4.53\\
\# Children in household aged 0-18 & 577.60 & 29.63 & 0.04 & -2.99 & 4.74\\
Peer exposure index & 577.74 & 30.19 & 0.03 & -3.06 & 4.68\\
\# Children in household aged 1-12 & 578.07 & 29.93 & 0.03 & -3.22 & 4.70\\
\addlinespace
Sibling variety score (Cassidy et al., 2005) & 578.13 & 29.87 & 0.03 & -3.25 & 4.67\\
Sibling variety score (Peterson, 2000) & 578.29 & 29.87 & 0.03 & -3.33 & 4.66\\
\# Household members & 578.80 & 30.40 & 0.02 & -3.59 & 4.53\\
Average hours spent in childcare per day & 579.36 & 30.74 & 0.02 & -3.87 & 4.60\\
\bottomrule
\end{tabular}}
\end{table}

Note that we did not find a great difference in WAIC scores between the compared models (see Supplements for WAIC scores and weights). The model estimates were all considerably smaller than estimates of age, study version and data collection, and all 95\% CIs included zero. Nevertheless, a general pattern emerges: exposure to a more variable social environment positively influenced children's gaze understanding. The number of people and, more specifically, children, as well as the more diverse their age, the more likely children were to understand the agent's gaze cue. The only predictor resulting in a negative estimate was the age at which a participant entered childcare, i.e., the later a child entered, the better performance in the task. Effect sizes were probably influenced by the lack of variance in the predictors: variables like household size and number of siblings typically vary very little among German households (see distribution characteristics of predictor variables below).

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrrrrrr}
\toprule
  & n & mean & sd & min & max & skew & kurtosis & se\\
\midrule
Age of childcare entry in months & 109 & 14.96 & 5.54 & 1.0 & 40 & 1.72 & 5.65 & 0.53\\
Average hours spent in childcare per day & 109 & 7.50 & 0.92 & 3.5 & 9 & -0.67 & 1.92 & 0.09\\
\# Household members & 109 & 3.72 & 0.92 & 2.0 & 7 & 0.30 & 0.49 & 0.09\\
\# Children in household aged 0-18 & 109 & 0.83 & 0.79 & 0.0 & 4 & 0.87 & 1.09 & 0.08\\
\# Children in household aged 1-12 & 109 & 0.69 & 0.74 & 0.0 & 4 & 1.23 & 2.67 & 0.07\\
\addlinespace
Sibling variety score (Peterson, 2000) & 109 & 0.60 & 0.56 & 0.0 & 2 & 0.23 & -0.87 & 0.05\\
Sibling variety score (Cassidy et al., 2005) & 109 & 0.63 & 0.54 & 0.0 & 2 & 0.18 & -0.70 & 0.05\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{receptive-vocabulary}{%
\subsection{Receptive vocabulary}\label{receptive-vocabulary}}

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

Our sample consisted of 117 children, including 11 3-year-olds (mean = 45.05 months, SD = 1.58, range = 43 - 47,
26 4-year-olds (mean = 53.17 months, SD = 3.01, range = 48 - 57),
32 5-year-olds (mean = 65.80 months, SD = 3.23, range = 61 - 71),\\
36 6-year-olds (mean = 78.36 months, SD = 3.26, range = 72 - 84), and 12 7-year-olds (mean = 88.11 months, SD = 1.96, range = 84 - 91).

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

We employed the oREV, an Item Response Theory based open receptive vocabulary task for 3 to 8-year-old children (Bohn, Prein, Delikaya, Haun, \& Gagarina, 2022). Similarly to the TANGO, the task was presented as an interactive web application (see Figure \ref{fig:fig5}; live demo \url{https://ccp-odc.eva.mpg.de/orev-demo/}; source code \url{https://github.com/ccp-eva/orev-demo}).

Each trial presented four pictures: one target word alongside three distractors (1 phonological, 1 semantic, 1 unrelated distractor). A verbal prompt asked children to select one of the pictures (prompt: ``Zeige mir {[}target word{]}''; engl.: ``Show me {[}target word{]}''). The positioning of the target word and the three distractor types was counterbalanced across the four display positions (upper/lower and left/right corners). Children responded by clicking on one of the four pictures. The outcome measure consisted of the proportion of correct responses.

\begin{figure}

{\centering \includegraphics[width=1\linewidth]{../figures/orev_procedure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\usepackage{setspace}
\usepackage{float}
\captionsetup[figure]{font={stretch=1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'},
  pdfauthor={Julia Prein1, Luke Maurits1, Annika Werwach1, Daniel B. M. Haun1,*, \& Manuel Bohn1,2,*},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Supplements for the manuscript `Variation in gaze understanding across the life span: A process-level perspective'}
\author{Julia Prein\textsuperscript{1}, Luke Maurits\textsuperscript{1}, Annika Werwach\textsuperscript{1}, Daniel B. M. Haun\textsuperscript{1,*}, \& Manuel Bohn\textsuperscript{1,2,*}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany\\\textsuperscript{2} Institute of Psychology, Leuphana University Lüneburg, Germany\\\textsuperscript{*} shared last authorship}

\hypertarget{study-1-lifespan}{%
\section{Study 1: Lifespan}\label{study-1-lifespan}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{rlrlr}
\toprule
Age group & n & Age mean & Age range & Age SD\\
\midrule
3 & 19 (7 female) & 3.62 & 3.04 - 3.99 & 0.31\\
4 & 17 (9 female) & 4.45 & 4.05 - 4.91 & 0.30\\
5 & 22 (13 female) & 5.56 & 5.08 - 5.99 & 0.31\\
6 & 24 (16 female) & 6.50 & 6.1 - 6.99 & 0.28\\
7 & 39 (20 female) & 7.48 & 7.04 - 7.95 & 0.25\\
\addlinespace
8 & 41 (20 female) & 8.46 & 8.03 - 8.98 & 0.27\\
9 & 56 (29 female) & 9.46 & 9.01 - 9.96 & 0.28\\
10 & 35 (22 female) & 10.49 & 10.01 - 11 & 0.28\\
11 & 54 (26 female) & 11.43 & 11.01 - 11.96 & 0.28\\
12 & 43 (19 female) & 12.41 & 12.01 - 12.99 & 0.30\\
\addlinespace
13 & 42 (19 female) & 13.50 & 13.09 - 13.99 & 0.27\\
14 & 20 (14 female) & 14.37 & 14.05 - 14.98 & 0.23\\
15 & 21 (11 female) & 15.56 & 15.05 - 15.98 & 0.30\\
16 & 19 (10 female) & 16.51 & 16.17 - 16.97 & 0.24\\
17 & 19 (10 female) & 17.53 & 17.01 - 17.95 & 0.28\\
\addlinespace
18 & 2 (0 female) & 18.00 & 18 - 18 & 0.00\\
19 & 5 (4 female) & 19.00 & 19 - 19 & 0.00\\
20 & 40 (25 female) & 23.02 & 20 - 29 & 2.77\\
30 & 40 (21 female) & 34.42 & 30 - 39 & 3.00\\
40 & 40 (24 female) & 44.17 & 40 - 49 & 2.92\\
\addlinespace
50 & 40 (21 female) & 54.38 & 50 - 59 & 3.04\\
60 & 40 (21 female) & 63.73 & 60 - 69 & 2.56\\
70 & 40 (20 female) & 72.75 & 70 - 79 & 2.44\\
\bottomrule
\end{tabular}}
\end{table}

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

\hypertarget{model-structures}{%
\subsubsection{Model structures}\label{model-structures}}

In the paper, we reported the following model structures: linear model: \texttt{mean\_imprecision\ \textasciitilde{}\ age\_centered}; quadratic model in \texttt{R:\ mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)}; cubic model: \texttt{mean\_imprecision\ \textasciitilde{}\ 1\ +\ age\_centered\ +\ I(age\_centered\^{}2)\ +\ I(age\_centered\^{}3);} Gaussian process model: \texttt{mean\_imprecision\ \textasciitilde{}\ gp(age\_centered,\ k=50,\ c=5/4,\ scale=TRUE)}. Note the additional parameters in the Gaussian process model. With the default settings, the underlying Gaussian process maths would get solved exactly. By providing the arguments \texttt{k} and \texttt{c}, we use an approximation process. The higher the value of k, the better the approximation: we have used \texttt{k=50} for faster processing speed and better diagnostics. \texttt{brms} suggests 5/4 as a value for \texttt{c}. Adding \texttt{scale=TRUE} is supposed to improve sampling speed and convergence.

Originally, we fitted the models on a trial-by-trial basis with the following structure in \texttt{R:\ performance\ \textasciitilde{}\ age\ +\ symmetricPosition\ +\ trialNr\ +\ (1\ +\ symmetricPosition\ +\ trialNr\ \textbar{}\ subjID)}. However, the Gaussian Process model was computationally heavy. Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect. We then visually compared the model predictions of the original and the simplified models with each other. As you can see in Figure \ref{fig:fig1}, results of the two models did not differ notably.

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{../figures/supplements_lifespan_modelstructure}

@@

\caption{\textbf{Comparison between models on a trial- or subject-level}. Grey dots show data of each trial. Solid lines show the mean predicted developmental trajectory for both models. Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).}\label{fig:fig1}
\end{figure}

\hypertarget{changepoint-analysis}{%
\subsubsection{Changepoint analysis}\label{changepoint-analysis}}

In our Bayesian changepoint analysis, we restricted the model to a constant mean (i.e., a flat line with zero degree polynomial) within each segment, and to have minimally 10 data points between two change points (i.e., corresponding to half of the data points we collected per adult decade) to avoid ``overreactions'' to individual outlying data points. In a supplementary analysis, we assessed how different parameter settings effected of our changepoint analysis. We changed the number of allowed change points, the minimum number of data points between change points, and the polynomial order. When the model had more explorative room, for example, by a greater number of change points, smaller minimum number of data points between change points, higher polynomial order, the model outputs showed more fine-grained change points. The exact location of the change points varied slightly. Overall, the interpretation stayed the same as the one we reported in the paper. While early childhood was characterized by much change, adults showed a relatively stable level of imprecision. There was a minor change in that elderly adults became slightly more imprecise again. If you are interested into the details, please have a look at the file \texttt{supplements\_changepoint\_parameters.html}, which you can find in the GitHub repository in the \texttt{stats} folder.

\hypertarget{study-2-computational-cognitive-model}{%
\section{Study 2: Computational cognitive model}\label{study-2-computational-cognitive-model}}

\hypertarget{analysis-1}{%
\subsection{Analysis}\label{analysis-1}}

\hypertarget{gaze-model-prediction}{%
\subsubsection{Gaze model prediction}\label{gaze-model-prediction}}

Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides). Since the task is presented on a screen, there is a natural border towards one side. Imagine the target lands to the very right side. Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now. Therefore, the predicted U-shaped pattern should decrease again towards the screen borders. For previous reliability analyses (Prein, Kalinke, Haun, \& Bohn, 2023), we had increased the trial number for an adult sample (N = 70; each 30 trials). Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \ref{fig:fig2}).

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{../figures/gazefunnel_adults}

@@

\caption{\textbf{Gaze funnel for adult sample with higher trial number}.}\label{fig:fig2}
\end{figure}

\hypertarget{inference-parameter-estimates-per-individual}{%
\subsection{Inference parameter estimates per individual}\label{inference-parameter-estimates-per-individual}}

As can be seen in Figure \ref{fig:fig3} and Figure \ref{fig:fig4}, the gaze model estimated the inference parameter for each individual. Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty. In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_facetedinference}

@@

\caption{\textbf{Gaze model estimates faceted by individual}.}\label{fig:fig3}
\end{figure}

\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{../figures/supplements_gazemodel_indinference}

\caption{\textbf{Gaze model estimates ordered by descending inference parameter value}.}\label{fig:fig4}
\end{figure}

@@

\hypertarget{study-3-components-of-gaze-understanding}{%
\section{Study 3: Components of gaze understanding}\label{study-3-components-of-gaze-understanding}}

\hypertarget{procedure-theory-of-mind-battery}{%
\subsection{Procedure Theory of mind battery}\label{procedure-theory-of-mind-battery}}
